Accelerating eigenvector and pseudospectra computation using blocked multi-shift triangular solves

### 2016-07-14 mstrsmPaper.tex
adding algorithm for generalized mstrsm

    \State \(s := \left[1, \cdots, 1 \right]^T\)

@@

@@

    \State \(s := t* s\)

@@

>>>>

    \State \(s := \left[1, \cdots, 1 \right]^T\) \Comment \(n\) entries

@@

    \State \(s(j) := t * s(j)\)

@@

    \State \(s(j) := t* s(j)\)

@@

\section{Generalized Multi-Shift Triangular Solve}
We introduce a final, generalized variant of the multi-shift
triangular solve problem. Given \(m\times m\) upper triangular
matrices \(U\) and \(V\), right-hand side vectors \(b_1,\cdots,b_n\),
and shifts \(\lambda_1,\cdots,\lambda_n\), we seek nonzero solution
vectors \(x_1,\cdots,x_n\) such that
\begin{align}
  \left( U - \lambda_j V \right) x_j &= b_j .
\end{align}
This problem can be solved with a slight modification of Algorithm
\ref{algorithm:multi-shift trsm}:
\begin{algorithm}[H]
  \label{algorithm:generalized multi-shift trsm}
  \caption{Generalized multi-shift triangular solve with blocked back substitution}
  \begin{algorithmic}
    \Procedure{GeneralizedMultiShiftTrsm}{$U, V, \lambda, B $}
    \Comment \(B\) is overwritten with \(X\)

    \State \(U' := U(\mathcal{I}_1,\mathcal{I}_1)-\lambda(j) * V(\mathcal{I}_1,\mathcal{I}_1)\) \Comment \texttt{xAXPY}

    \State \Call{Trsv}{$U', B(\mathcal{I}_1,j)$} 
    \Comment Diagonal block step (\texttt{xTRSV})

    \State \( C(:,j) := \lambda(j) * B(\mathcal{I}_1,j)\) \Comment \texttt{xSCAL}

    \State \( B(\mathcal{I}_0,:) := B(\mathcal{I}_0,:) + V(\mathcal{I}_0,\mathcal{I}_1)* C \) \Comment \texttt{xGEMM}

    \EndProcedure
  \end{algorithmic}
\end{algorithm}
\noindent
